\begin{abstract}
This paper presents a digitally assisted foreground calibration method for a low-cost geophone analog front end implemented in a PSoC~5LP. The front end adapts a previously reported analog compensation topology to an inexpensive mixed-signal platform. However, the offset and drift of its on-chip operational amplifiers are multiplied by the cascaded gain stages, reducing the available dynamic range and eventually driving intermediate nodes into saturation. A fixed DC correction at the summing stage is functional but cannot restore the operating points of the remaining stages. The proposed method sequentially observes every stage through an on-chip analog multiplexer and reuses the 18-bit delta-sigma converter employed for geophone acquisition. ADC measurements are rescaled into a DAC-equivalent control domain, and a foreground control algorithm adjusts four independent 8-bit VDAC references. A discrete-time PI controller with deadband and anti-windup was selected as a simple implementation, but the architecture is not restricted to this controller. The digital filter hardware already used for acquisition is temporarily reconfigured to estimate the DC component. Once the four stages have converged, the DAC values are frozen during acquisition and may be stored in EEPROM for each programmable-gain setting. Preliminary bench observations showed uncompensated drifts on the order of volts, whereas calibrated stage outputs remained approximately within $\pm100$~mV. \textcolor{draftred}{Controlled measurements must replace this preliminary observation with: initial and residual offset, unclipped input-range improvement, convergence time, and successful calibration runs.}
\end{abstract}

\begin{IEEEkeywords}
analog front end, automatic calibration, DC offset, geophone, mixed-signal systems, programmable system-on-chip, PSoC
\end{IEEEkeywords}

\todoexp{ESTE ES UN BORRADOR INTERNO. Antes de enviar se deben completar los valores cuantitativos, reemplazar las cajas de figuras y eliminar todas las anotaciones rojas y amarillas. El artículo definitivo ya está escrito en inglés, como exige URUCON.}
