\section{Introduction}

Multichannel surface-wave methods use spatially distributed vibration measurements to estimate the dispersive behavior of Rayleigh waves and infer near-surface mechanical properties \cite{Park1999,Foti2014}. Although the processing methods are well established, the acquisition hardware remains a significant part of the cost and deployment complexity. Compact wireless nodes built from inexpensive geophones and mixed-signal microcontrollers are therefore attractive for dense and reconfigurable arrays \cite{Kafadar2020}.

The present work forms part of a low-cost Internet-of-Things acquisition platform based on SM-24 moving-coil geophones. A PSoC~5LP was selected as the analog front end because it integrates programmable-gain amplifiers, operational amplifiers, analog filters, voltage DACs, analog multiplexers, a delta-sigma ADC, a digital filter block, DMA, and an Arm Cortex-M3 processor in a single device \cite{InfineonPSoC}. In the proposed implementation, the same ADC and digital filter are time-shared between geophone acquisition and front-end calibration. This resource reuse avoids a separate calibration converter or processor. The same reconfigurability that makes the device attractive also imposes a limitation: its internal analog blocks cannot be selected independently for low offset, low drift, and low flicker noise. Lopin and Lopin reported the same tradeoff in a single-chip PSoC potentiostat, noting substantially poorer offset and voltage-noise specifications than those of purpose-selected external amplifiers \cite{Lopin2018}.

The geophone conditioning circuit used in this work is derived from the cascade correction and subtraction topology proposed by Ma \emph{et al.} \cite{Ma2023}. When mapped to the PSoC, accumulated DC errors prevented the use of sufficiently aggressive gain settings and became particularly severe at the ADDER output.

A continuously active DC servo was implemented and experimentally evaluated as an initial solution. Its performance exposed an unavoidable compromise: a very low servo bandwidth preserved the low-frequency vibration signal but required an impractically long centering time, whereas a faster loop disturbed the signal band. Moreover, every programmable-gain change altered the loop conditions and initiated a new transient. The proposed method therefore performs a finite foreground calibration before measurement and disconnects the controller afterward.

The contribution is threefold: 1) a per-stage analog calibration architecture that reuses the PSoC analog multiplexer, ADC, digital filter, and four VDACs; 2) a controller-independent formulation, demonstrated with a gain-aware PI implementation using deadband, anti-windup, slew limiting, stability detection, and one-LSB refinement; and 3) a measurement-gated operating policy that freezes all corrections before seismic data are recorded. Consequently, the calibration loop introduces no additional closed-loop poles into the acquisition transfer function.

%\draftfigure{22mm}{System context of the proposed geophone node and the scope of this paper.}{Dibujar: SM-24 $\rightarrow$ PSoC AFE autocalibrable $\rightarrow$ ADC/DMA $\rightarrow$ ESP32 esclavo $\rightarrow$ ESP-NOW $\rightarrow$ maestro/interfaz. Resaltar con color solamente el PSoC, porque es la contribución del artículo.}

