\section{Discussion}
\label{sec:discussion}

The method trades component precision for system-level measurement and digital assistance, unlike precision front ends characterized near the sensor's Johnson-noise limit \cite{Kirchhoff2017}. Its benefit is not that the ADC output has zero mean -- a software subtraction could do that -- but that the DACs modify the physical operating points before large downstream gains apply, so the correction is agnostic to the error source, provided the stage is measurable and the DAC has sufficient authority and range.

The foreground method replaced a tested continuous DC servo: a low corner settled impractically slowly, a higher corner interfered with the signal, and each gain change restarted the transient, matching the corner-frequency/settling tradeoff reported for DC-servo compensation \cite{Liu2020}. The proposed controller disconnects during acquisition, holding the DAC outputs constant and adding no time-varying feedback or servo poles. EEPROM avoids most full runs while the errors remain repeatable; if aging, temperature, or another condition moves a stored point outside tolerance, verification rejects it and recalibrates at boot, after a gain change, or on command (Section~\ref{sec:self-calibration}). Remaining limitations are finite DAC resolution, no correction of noise or distortion, and unvalidated convergence under sustained vibration or thermal drift.

\subsection{The PGA Stage: A Partial Result, Explained}
\label{sec:pga-note}

Unlike BP, SUM, and LP, the PGA stage's post-calibration offset is not consistently much smaller than Default: the mean $|\text{offset}|$ falls only modestly at low gain and by roughly half at best. The observed behavior is consistent with two firmware choices. First, the deadband $\Delta_i$ (Section~\ref{sec:self-calibration}) is an acceptance margin, not a physical limit. On Board~B at $\times4$, the default PGA offset fell inside the normal deadband on every run attempted, and the controller declared convergence without moving the DAC. Tightening the deadband by hand caused the controller to act, directly confirming deadband-gated convergence in that condition. Second, the 128-sample FIR estimator trades residual resolution against convergence time; whether a longer estimator materially improves the remaining PGA offset was not tested. The deadband intervention rules out a fixed PGA hardware floor in the tested condition, and neither effect compromises the final-stage headroom target in Table~\ref{tab:results}.

The two orange cells in Table~\ref{tab:results} occur where the fixed-reference offset was already below 1\%FS: BP at $\times1$ and SUM at $\times50$ on Board~A. Their Proposed values remain at or below 1.2\%FS. The controller is designed to enter an acceptance band, not to guarantee a lower sample mean in every repeated cell, so these small reversals do not contradict the headroom result.

Fig.~\ref{fig:calibration_trace} shows the sequential PGA~$\rightarrow$~BP~$\rightarrow$~SUM~$\rightarrow$~LP correction: each measured output steps when addressed and then holds. The four-stage sequence takes approximately 10~s typical; the Table~\ref{tab:cal_params} timeouts sum to 57.6~s only if every stage times out, which was not observed.

The two boards have markedly different Default operating points, yet both satisfy the headroom target at their reported settings. Feedforward values were tuned only on Board~B at $\times50$; Board~A received no manual adjustment and still converged across its tested gains. This supports reuse of one nominal initialization in a dense network, with the loop absorbing unit- and gain-dependent variation. The $N{=}10$ runs quantify within-cell repeatability, but two boards cannot establish population-level scaling; more units and cross-temperature trials are required.
