\section{Conclusion}

A per-stage foreground self-calibration method was developed for a low-cost PSoC-based geophone front end. Four internal VDACs, an analog multiplexer, the acquisition delta-sigma ADC, an otherwise-idle hardware filter, and a configurable PI controller adjust each observable stage's operating point within the available DAC range and resolution. Unlike an ADDER-only patch, the method addresses offsets before and after the summing node; unlike the continuously active servo tested during development, it adds no servo poles or settling-time-versus-distortion compromise. Stored gain-dependent corrections make full recalibration infrequent, while automatic verification restores the measurement path without a full run when conditions have not changed.

Oscilloscope measurements on two independently assembled boards, across the PGA's full configurable gain range ($\times1$ to $\times50$), show the front end consistently kept within a few percent of the ADC's full-scale range after calibration, regardless of board or gain, down from as much as 46\% of full-scale uncalibrated. The PGA stage alone shows only partial convergence under some conditions, traced to the loop's deadband gating its response at that stage specifically rather than to a control-loop or hardware limitation; this does not affect the overall headroom result, which is set by the stages closer to the ADC. Calibration converges in approximately 10~s typical (57.6~s worst case) per run, acceptable since triggered once after deployment; field surface-wave records over a 10--50~m line demonstrate operation, not a quantitative calibrated-vs-uncalibrated comparison. A larger board population, cross-temperature characterization, whether the injected VDAC references affect the noise floor, and a controlled field calibrated-vs-uncalibrated comparison remain future work.

